Inequalities Witnessing Quantum Incompatibility in The Triangle Scenario

### 2016-09-15 document/main.tex
working draft
symmetries

% === Commonly re-occurring symbols ===
\newcommand{\hgraph}{\mathcal{H}}
\newcommand{\graph}{\mathcal{G}}
\newcommand{\nodes}{\mathcal{N}}
\newcommand{\weights}{\mathcal{W}}
\newcommand{\edges}{\mathcal{E}}
\newcommand{\trans}{\mathcal{T}}
\newcommand{\ind}{\mathcal{I}}
\newcommand{\perm}{\Omega}
\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\ancestralindep}{\perp}
\newcommand{\valprod}{\times}
\newcommand{\bigvalprod}{\prod}
\newcommand{\com}{\mathrel{\Yright\hspace{-0.2em}\Yleft}}
\newcommand{\ext}{\mathrel{\Yleft}}
\newcommand{\res}{\mathrel{\Yright}}
\newcommand{\gelem}{\varphi}
\newcommand{\action}[1]{\gelem\bs{#1}}
\newcommand{\mscenario}{\mathcal{M}}
\newcommand{\jointvar}{\mathcal{J}}
\newcommand{\mset}[1]{\gamma^{#1}}
\newcommand{\extmset}[1]{\Gamma^{#1}}
\newcommand{\supp}[1]{\si\br{#1}}

@@

% === To allow for labeling of rows and columns of a matrix ===
\usepackage{../packages/kbordermatrix}
\renewcommand{\kbldelim}{(} % Left delimiter
\renewcommand{\kbrdelim}{)} % Right delimiter

@@

    \section{The Fritz Distribution}
    \label{sec:fritz_dist}
    The \term{Fritz distribution} $P_F$ is a quantum-accessible distribution known to be incompatible with the Triangle Scenario \cite{Fritz_2012}. Explicitly, $P_F$ is a three-party ($A,B,C$), four-outcome ($1,2,3,4$) distribution that has form as follows:
    \begin{align*}
    \eq \label{eq:fritz_dist}
    \begin{split}
    \prob[F][111] = \prob[F][221] = \prob[F][412] = \prob[F][322] = \prob[F][233] = \prob[F][143] = \prob[F][344] = \prob[F][434] &= \f{1}{32}\br{2 + \sqrt{2}} \\
    \prob[F][121] = \prob[F][211] = \prob[F][422] = \prob[F][312] = \prob[F][243] = \prob[F][133] = \prob[F][334] = \prob[F][444] &= \f{1}{32}\br{2 - \sqrt{2}}
    \end{split}
    \end{align*}
    Here the notation $\prob[F][abc] = \prob[ABC][abc] = \prob[][A=a,B=b,C=c]$ is used. The Fritz distribution $\prob[F]$ can be realized with the following quantum configuration:
    \begin{equation}
    \begin{gathered}
    \label{eq:fritz_quantum_realization}
    \rho_{AB} = \ket{\Psi^+}\bra{\Psi^+} \quad \rho_{BC} = \rho_{CA} = \ket{\Phi^+}\bra{\Phi^+} \\
    M_{A} = \bc{\ket{0\psi_0}\bra{0\psi_0}, \ket{0\psi_{\pi}}\bra{0\psi_{\pi}}, \ket{1\psi_{-\pi/2}}\bra{1\psi_{-\pi/2}}, \ket{1\psi_{\pi/2}}\bra{1\psi_{\pi/2}}} \\
    M_{B} = \bc{\ket{\psi_{\pi/4}0}\bra{\psi_{\pi/4}0}, \ket{\psi_{5\pi/4}0}\bra{\psi_{5\pi/4}0}, \ket{\psi_{3\pi/4}1}\bra{\psi_{3\pi/4}1}, \ket{\psi_{-\pi/4}1}\bra{\psi_{-\pi/4}1}} \\
    M_{C} = \bc{\ket{00}\bra{00}, \ket{01}\bra{01}, \ket{10}\bra{10}, \ket{11}\bra{11}}
    \end{gathered}
    \end{equation}
    Where for convenience of notation $\psi_x$ is used to denote the superposition,
    \[ \ket{\psi_x} = \f{1}{\sqrt{2}}\br{\ket{0} + e^{ix}\ket{1}} \]
    Additionally $\ket{\Psi^+} = \f{1}{\sqrt{2}}\br{\ket{01} + \ket{10}}$ and $\ket{\Phi^+} = \f{1}{\sqrt{2}}\br{\ket{00} + \ket{11}}$ are two maximally entangled Bell states.

@@

    To illustrate this concretely, consider the following example:
    \begin{example}
        \label{ex:marginal_matrix}
        Let $\jointvar$ be $3$ binary variables $\jointvar = \bc{a,b,c}$ and consider the marginal scenario $\mscenario = \bc{\bc{a,c}, \bc{b}}$. The incidence matrix becomes:
        \[ M = \kbordermatrix{
            (a,b,c) \:\: \mapsto & (0,0,0) & (0,0,1) & (0,1,0) & (0,1,1) & (1,0,0) & (1,0,1) & (1,1,0) & (1,1,1) \\
            (a\mapsto0, c\mapsto0) & 1 & 0 & 1 & 0 & 0 & 0 & 0 & 0 \\
            (a\mapsto0, c\mapsto1) & 0 & 1 & 0 & 1 & 0 & 0 & 0 & 0 \\
            (a\mapsto1, c\mapsto0) & 0 & 0 & 0 & 0 & 1 & 0 & 1 & 0 \\
            (a\mapsto1, c\mapsto1) & 0 & 0 & 0 & 0 & 0 & 1 & 0 & 1 \\
            (b\mapsto0)            & 1 & 1 & 0 & 0 & 1 & 1 & 0 & 0 \\
            (b\mapsto1)            & 0 & 0 & 1 & 1 & 0 & 0 & 1 & 1
        } \]
    \end{example}

@@

    \begin{definition}
        Any hypergraph with strictly non-empty edges $\forall e \neq \emptyset$ will always admit the \term{trivial transversal} $\trans^*$ where all nodes are considered as members $\trans^* = \nodes$. Any hypergraph with empty edges will be called a \term{degenerate hypergraph} as it admits no transversals\footnote{Most authors require that all hypergraphs be non-degenerate \cite{Kavvadias_2005}.}.
    \end{definition}
    Remark \ref{remark:trivial_transversal} guarantees that all marginal hypergraphs are non-degenerate. There are two distinct approaches to hypergraph transversal generation: \textit{top-down} and \textit{bottom-up}.
    \begin{definition}
        A \term{top-down} hypergraph transversal generation refers to any algorithm that begins with the trivial transversal $\trans^*$ and iteratively removes unnecessary nodes from $\trans^*$.
    \end{definition}

@@

    One should select a top-down method if the typical size of minimal transversals $\abs{\trans}$ is comparable to the number of nodes $\abs{\nodes}$, otherwise a bottom-up method will perform better.
    For our purposes we implemented a deep-first transversal algorithm similar to
    Recalling \cref{remark:trivial_transversal}

@@

    \todo[TC]{Weighted transversals and Optimizations}
    \todo[TC]{Seeding inequalities (huge advantage here)}
    \section{Deriving Symmetric Inequalities}
    \label{sec:symmetry}
    Symmetric compatibility inequalities are useful for a number of reasons. First, Bancal et. al. \cite{Bancal_2010} discuss computational advantages in considering symmetric versions of marginal polytopes mentioned in \cref{sec:comp_con_mp}; the number of extremal points typically grows exponentially in $\jointvar$, but only polynomial for the symmetric polytope. They also note a number of interesting inequalities (such as CHSH \cite{CHSH_Original}) can be written in a way that is symmetric under the exchange of parties, demonstrating that quantum-non-trivial inequalities can be recovered from facets of a symmetric polytope. Second, numerical optimizations against inequalities invariant under exchange of parties will lead to one of two interesting cases: either the extremal distribution is invariant under exchange of parties or it is not. The latter case generates a family of incompatible distributions obtained by exchanging parties of the found extremal distribution\footnote{If the extremal distribution is not invariant under exchange of parties, there is indication that the space of accessible distributions is non-convex.}. In this section we discuss how to achieve computational advantage and its application to the inequality techniques mentioned in \cref{sec:certificate_inequalities} and \cref{sec:implication_inequalities}.
    \subsection{Causal Symmetry}
    The aim of this section is to formalize what types of symmetries are present in a particular causal structure $\graph$. The group of these causal symmetries will define, for each compatibility inequality $I_{\mscenario}$, a family of inequalities that are also valid incompatibility inequalities.

    First consider the permutation group acting on a set of nodes $N \subseteq \nodes$ denoted $\Perm{N}$ to be the set of all bijective maps $\gelem$ from $N$ to $N$.
    \[ \Perm{N} = \bc{\gelem \mid \gelem : N \to N} \]
    The action of $\gelem \in \Perm{N}$ on a causal structure $\graph$ is defined via an the extension of $\gelem$ to the corresponding element in $\Perm{\nodes}$ that leaves nodes $n \in \nodes \setminus N$ invariant,
    \begin{align*}
    \action{\graph} &\defined \br{\action{\nodes}, \action{\edges}} \\
    \action{\nodes} &\defined \bc{\action{n} \mid n \in \nodes} = \nodes \\
    \action{\edges} &\defined \bc{\action{e} \mid e \in \edges}
    \end{align*}
    To motivate a more general treatment of such symmetries, consider the Triangle Scenario of \cref{fig:triangle_scenario}. Due to the rotational and reflective symmetries of the Triangle Scenario, any permutation $\gelem \in \Perm{\nodes_O}$ of the observable nodes $\nodes_O = \bc{A, B, C}$ creates a new causal structure $\action{\graph}$ that is \textit{equivalent} to $\graph$ up to a relabeling of \textit{latent} nodes. By construction, any valid compatibility inequality $I_{\mscenario}$ for the marginal scenario $\mscenario = \bc{V_1, \ldots, V_k}$ is \textit{independent} of the labeling of latent nodes. Therefore applying $\gelem$ to all distributions in $I_{\mscenario}$ yields $\action{I_{\mscenario}} \defined \action{I}_{\action{\mscenario}}$, another valid compatibility inequality for the permuted marginal scenario $\action{\mscenario}$ defined as,
    \[ \action{\mscenario} = \bc{\action{V_1}, \ldots, \action{V_k}} \]
    % \begin{example}
    %     \todo[TC]{Above trivial example.}
    %     Consider the marginal scenario $V_{\bs{4}} = \bc{\bc{A,B,C}, \bc{A}, \bc{B}, \bc{C}}$ and the compatibility inequality $I_{\bc{ABC, A, B, C}}$ for the Triangle Scenario in \cref{fig:triangle_scenario} with the following form,
    %     \[ \prob[ABC][002]\prob[ABC][003] \leq \prob[A][0]\prob[C][3] \]
    %     Now consider $\gelem = \bc{A \to A, B \to C, C \to B}$. Since $\action{\graph} = \graph$, $\action{I_{\mscenario}}$ is also a valid compatibility inequality,
    % \end{example}
    More generically, any permutation $\gelem$ that preserves the graphical structure of $\graph$ can be applied to $I_{\mscenario}$ to generate new and valid compatibility inequalities. Specifically this alludes to the \term{graph automorphism group} $\Aut{\graph}$ of $\graph$.
    \[ \Aut{\graph} \defined \bc{\gelem \in \Perm{\nodes} \mid \action{\graph} = \graph} \]
    In general, $\Aut{\graph}$ could include elements $\gelem$ that map latent nodes to observable nodes\footnote{In practice however, it is rare to be considering a causal structure $\graph$ where some latent node $n_L \in \nodes_L$ takes on an role indistinguishable from some observable node $n_O \in \nodes_O$, so this won't be an issue.}. This behaviour is \textit{undesired} for causal inference where the latent nodes will never appear in a marginal scenario. Instead, the subgroup of $\Aut{\graph}$ that never maps observable nodes to latent nodes is the \term{set-wise stabilizer} of $\Aut{\graph}$ for $\nodes_O$ and will be expressed with a subscript.

    \begin{definition}
        The \term{causal symmetry group} for a causal structure $\graph$ is the graph automorphism subgroup that stabilizes the observable nodes.
        \[ \Aut[\nodes_O]{\graph} = \bc{\gelem \in \Perm{\nodes} \mid \action{\graph} = \graph, \forall n \in \nodes_O :\action{n} \in \nodes_O} \]
        Given any compatibility inequality $I_{\mscenario}$, each element $\gelem$ of the causal symmetry group defines a new valid compatibility inequality $\action{I_{\mscenario}} = \action{I}_{\action{\mscenario}}$.
    \end{definition}

    The inflation technique discussed in \cref{sec:summary_inflation} allows one to derive compatibility inequalities for a causal structure $\graph$ by considering the marginal problem over the pre-injectable sets of $\graph'$ denoted $\PreInj[\graph]{\graph'} = \bc{V_1, \ldots, V_k}$. It is important to recall that due to \cref{lem:inflation}, inequalities $I'$ for $\graph'$ are \textit{only} transferable to inequalities $I$ for $\graph$ if $I'$ is in terms of distributions over the pre-injectable sets $I'_{\PreInj[\graph]{\graph'}}$. As a consequence of this observation, we need to consider a subgroup of the causal symmetry group that preserves the pre-injectable sets,
    \[ \action{\PreInj[\graph]{\graph'}} = \PreInj[\graph]{\graph'} \eq \label{eq:preserved_preinj} \]

    \begin{definition}
        The \term{restricted causal symmetry group} $\Phi$ for a causal structure $\graph$ and a marginal scenario $\mscenario$ is the graph automorphism subgroup that stabilizes the marginal scenario $\mscenario$.
        \[ \Phi \defined \Aut[\mscenario]{\graph} = \bc{\gelem \in \Perm{\nodes} \mid \action{\graph} = \graph, \forall V \in \mscenario : \action{V} \in \mscenario} \]
        Given any compatibility inequality $I_{\mscenario}$ each element $\gelem$ of the causal symmetry group defines a new valid compatibility inequality $\action{I_{\mscenario}} = \action{I}_{\mscenario}$ over the \textit{same} marginal context $\mscenario$.
    \end{definition}

    The restricted causal symmetry group for the pre-injectable sets of an inflation $\graph'$ is the ideal symmetry group for use with the inflation technique. If one obtains a particular inequality $I'_{\PreInj[\graph]{\graph'}}$ as well as the restricted causal symmetry group $\Phi$, an entire family of valid compatibility inequalities are also obtained.
    \[ \bc{\action{I'}_{\PreInj[\graph]{\graph'}} \mid \gelem \in \Phi} \text{ where } \Phi = \Aut[\PreInj[\graph]{\graph'}]{\graph'} \]
    We have obtained $\Phi$ for the inflated triangle scenario \cref{fig:inflated_triangle_scenario}. $\Phi$ is an order $48$ group with the following $4$ generators:

>>>>

% === To allow for labeling of rows and columns of a matrix ===
\usepackage{kbordermatrix}
\renewcommand{\kbldelim}{(} % Left delimiter
\renewcommand{\kbrdelim}{)} % Right delimiter

% === Commonly re-occurring symbols ===
\newcommand{\hgraph}{\mathcal{H}}
\newcommand{\graph}{\mathcal{G}}
\newcommand{\nodes}{\mathcal{N}}
\newcommand{\weights}{\mathcal{W}}
\newcommand{\edges}{\mathcal{E}}
\newcommand{\trans}{\mathcal{T}}
\newcommand{\ind}{\mathcal{I}}
\newcommand{\netperm}{\Pi}
\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\ancestralindep}{\perp}
\newcommand{\valprod}{\times}
\newcommand{\bigvalprod}{\prod}
\newcommand{\com}{\mathrel{\Yright\hspace{-0.2em}\Yleft}}
\newcommand{\ext}{\mathrel{\Yleft}}
\newcommand{\res}{\mathrel{\Yright}}
\newcommand{\gep}{\varphi}
\newcommand{\gp}{\Phi}
\newcommand{\geo}{\omega}
\newcommand{\go}{\Omega}
\newcommand{\mscenario}{\mathcal{M}}
\newcommand{\jointvar}{\mathcal{J}}
\newcommand{\mset}[1]{\gamma^{#1}}
\newcommand{\extmset}[1]{\Gamma^{#1}}
\newcommand{\supp}[1]{\si\br{#1}}

@@

@@

    \section{The Fritz Distribution}
    \label{sec:fritz_dist}
    The \term{Fritz distribution} $P_F$ is a quantum-accessible distribution known to be incompatible with the Triangle Scenario \cite{Fritz_2012}. Explicitly, $P_F$ is a three-party ($A,B,C$), four-outcome ($1,2,3,4$) distribution that has form as follows:
    \begin{align*}
    \eq \label{eq:fritz_dist}
    \begin{split}
    \prob[F][111] = \prob[F][221] = \prob[F][412] = \prob[F][322] = \prob[F][233] = \prob[F][143] = \prob[F][344] = \prob[F][434] &= \f{1}{32}\br{2 + \sqrt{2}} \\
    \prob[F][121] = \prob[F][211] = \prob[F][422] = \prob[F][312] = \prob[F][243] = \prob[F][133] = \prob[F][334] = \prob[F][444] &= \f{1}{32}\br{2 - \sqrt{2}}
    \end{split}
    \end{align*}
    Here the notation $\prob[F][abc] = \prob[ABC][abc] = \prob[][A=a,B=b,C=c]$ is used. The Fritz distribution $\prob[F]$ can be realized with the following quantum configuration:
    \begin{equation}
    \begin{gathered}
    \label{eq:fritz_quantum_realization}
    \rho_{AB} = \ket{\Psi^+}\bra{\Psi^+} \quad \rho_{BC} = \rho_{CA} = \ket{\gp^+}\bra{\gp^+} \\
    M_{A} = \bc{\ket{0\psi_0}\bra{0\psi_0}, \ket{0\psi_{\pi}}\bra{0\psi_{\pi}}, \ket{1\psi_{-\pi/2}}\bra{1\psi_{-\pi/2}}, \ket{1\psi_{\pi/2}}\bra{1\psi_{\pi/2}}} \\
    M_{B} = \bc{\ket{\psi_{\pi/4}0}\bra{\psi_{\pi/4}0}, \ket{\psi_{5\pi/4}0}\bra{\psi_{5\pi/4}0}, \ket{\psi_{3\pi/4}1}\bra{\psi_{3\pi/4}1}, \ket{\psi_{-\pi/4}1}\bra{\psi_{-\pi/4}1}} \\
    M_{C} = \bc{\ket{00}\bra{00}, \ket{01}\bra{01}, \ket{10}\bra{10}, \ket{11}\bra{11}}
    \end{gathered}
    \end{equation}
    Where for convenience of notation $\psi_x$ is used to denote the superposition,
    \[ \ket{\psi_x} = \f{1}{\sqrt{2}}\br{\ket{0} + e^{ix}\ket{1}} \]
    Additionally $\ket{\Psi^+} = \f{1}{\sqrt{2}}\br{\ket{01} + \ket{10}}$ and $\ket{\gp^+} = \f{1}{\sqrt{2}}\br{\ket{00} + \ket{11}}$ are two maximally entangled Bell states.

@@

    To illustrate this concretely, consider the following example:
    \begin{example}
        \label{ex:marginal_matrix}
        Let $\jointvar$ be $3$ binary variables $\jointvar = \bc{a,b,c}$ and consider the marginal scenario $\mscenario = \bc{\bc{a,b}, \bc{b,c}, \bc{a,c}}$. The incidence matrix becomes:
        \newcommand{\kone}{\mathbf{1}}
        \newcommand{\kzer}{\textcolor{gray}{0}}
        \[ M = \kbordermatrix{
            (a,b,c) \:\: \mapsto & (0,0,0) & (0,0,1) & (0,1,0) & (0,1,1) & (1,0,0) & (1,0,1) & (1,1,0) & (1,1,1) \\
            (a\mapsto0, b\mapsto0) & \kone & \kone & \kzer & \kzer & \kzer & \kzer & \kzer & \kzer \\
            (a\mapsto0, b\mapsto1) & \kzer & \kzer & \kone & \kone & \kzer & \kzer & \kzer & \kzer \\
            (a\mapsto1, b\mapsto0) & \kzer & \kzer & \kzer & \kzer & \kone & \kone & \kzer & \kzer \\
            (a\mapsto1, b\mapsto1) & \kzer & \kzer & \kzer & \kzer & \kzer & \kzer & \kone & \kone \\
            (b\mapsto0, c\mapsto0) & \kone & \kzer & \kzer & \kzer & \kone & \kzer & \kzer & \kzer \\
            (b\mapsto0, c\mapsto1) & \kzer & \kone & \kzer & \kzer & \kzer & \kone & \kzer & \kzer \\
            (b\mapsto1, c\mapsto0) & \kzer & \kzer & \kone & \kzer & \kzer & \kzer & \kone & \kzer \\
            (b\mapsto1, c\mapsto1) & \kzer & \kzer & \kzer & \kone & \kzer & \kzer & \kzer & \kone \\
            (a\mapsto0, c\mapsto0) & \kone & \kzer & \kone & \kzer & \kzer & \kzer & \kzer & \kzer \\
            (a\mapsto0, c\mapsto1) & \kzer & \kone & \kzer & \kone & \kzer & \kzer & \kzer & \kzer \\
            (a\mapsto1, c\mapsto0) & \kzer & \kzer & \kzer & \kzer & \kone & \kzer & \kone & \kzer \\
            (a\mapsto1, c\mapsto1) & \kzer & \kzer & \kzer & \kzer & \kzer & \kone & \kzer & \kone
        } \]
    \end{example}

@@

    \begin{definition}
        Any hypergraph with strictly non-empty edges $\forall e \neq \emptyset$ will always admit the \term{trivial transversal} $\trans^*$ where all nodes are considered as members $\trans^* = \nodes$. Any hypergraph with empty edges will be called a \term{degenerate hypergraph} as it admits no transversals\footnote{Most authors require that all hypergraphs be non-degenerate \cite{Kavvadias_2005}.}.
    \end{definition}
    Remark ?? guarantees that all marginal hypergraphs are non-degenerate. There are two distinct approaches to hypergraph transversal generation: \textit{top-down} and \textit{bottom-up}.
    \begin{definition}
        A \term{top-down} hypergraph transversal generation refers to any algorithm that begins with the trivial transversal $\trans^*$ and iteratively removes unnecessary nodes from $\trans^*$.
    \end{definition}

@@

    One should select a top-down method if the typical size of minimal transversals $\abs{\trans}$ is comparable to the number of nodes $\abs{\nodes}$, otherwise a bottom-up method will perform better.
    For our purposes we implemented a deep-first transversal algorithm similar to
    Recalling

@@

    \todo[TC]{Weighted transversals and Optimizations}
    \todo[TC]{Seeding inequalities (huge advantage here)}
    \section{Marginal Symmetries}
    \label{sec:symmetry}
    Symmetric compatibility inequalities are useful for a number of reasons. First, Bancal et. al. \cite{Bancal_2010} discuss computational advantages in considering symmetric versions of marginal polytopes mentioned in \cref{sec:comp_con_mp}; the number of extremal points typically grows exponentially in $\jointvar$, but only polynomial for the symmetric polytope. They also note a number of interesting inequalities (such as CHSH \cite{CHSH_Original}) can be written in a way that is symmetric under the exchange of parties, demonstrating that quantum-non-trivial inequalities can be recovered from facets of a symmetric polytope. Second, numerical optimizations against inequalities invariant under exchange of parties will lead to one of two interesting cases: either the extremal distribution is invariant under exchange of parties or it is not. The latter case generates a family of incompatible distributions obtained by exchanging parties of the found extremal distribution\footnote{If the extremal distribution is not invariant under exchange of parties, there is indication that the space of accessible distributions is non-convex.}. In this section we discuss how to exploit symmetries in the extension covering procedure in order to reduce the computational search space. \\

    To demonstrate what kinds of symmetries are valid, we present the following example:
    \begin{example}
        \label{ex:symmetries}
        First consider the marginal scenario $\mscenario = \bc{\bc{a, b, c}, \bc{c, d}, \bc{a, d}}$ where each variable in $\jointvar = \bc{a,b,c,d}$ is binary. Moreover, let $I_{\mscenario}$ be the compatibility inequality,
        \[ I_{\mscenario} = \bc{\prob[abc][010] \leq \prob[cd][00] + \prob[ad][01]}  \]
        Intuitively, a compatibility is independent of outcome labels $O_a = O_b = O_c = O_d = \bc{0,1}$. Therefore new compatibility inequalities can be generated from $I_{\mscenario}$ by permuting its outcome labels. Let $\geo_v : O_v \to O_v : \bc{0,1} \mapsto \geo_v\bs{\bc{0,1}} = \bc{1,0}$ be a permutation of the outcome labels for variable $v$. Let $\geo = \geo_a \times \geo_c$ be the permutation of variables $a$ and $c$. The action of $\geo$ on outcome labels induces an action on the inequality $I_{\mscenario}$ itself,
        \begin{align*}
        \geo\bs{I_{\mscenario}} &= \bc{\prob[abc][\geo\bs{010}] \leq \prob[cd][\geo\bs{00}] + \prob[ad][\geo\bs{01}]} \\
        &= \bc{\prob[abc][111] \leq \prob[cd][10] + \prob[ad][11]}
        \end{align*}
        The new inequality $\geo\bs{I_{\mscenario}}$ is also a valid compatibility inequality. By construction, any permutation $\geo$ over outcome labels leaves the marginal scenario invariant ($\geo\bs{\mscenario} = \mscenario$) and thus we may write $\geo\bs{I_{\mscenario}} = \geo\bs{I}_{\mscenario}$. \\

        Alternatively, permutations of the variables themselves are also permitted. Let $\gep : \jointvar \to \jointvar : \bc{a,b,c,d} \mapsto \gep\bs{\bc{a,b,c,d}} = \bc{c,a,d,b}$ be a permutation of the variables $\jointvar$. Intuitively $\gep$ acts on $I_{\mscenario}$ in the following way,
        \begin{align*}
        \gep\bs{I_{\mscenario}} &= \bc{\prob[\gep\bs{abc}][010] \leq \prob[\gep\bs{cd}][00] + \prob[\gep\bs{ad}][01]} \\
        &= \bc{\prob[cad][010] \leq \prob[db][00] + \prob[cb][01]} \\
        &= \bc{\prob[acd][100] \leq \prob[bd][00] + \prob[bc][10]}
        \end{align*}
        In general (as in this example), permutations over all variables can modify the marginal scenario $\gep\bs{\mscenario} \neq \mscenario$; in general we write $\gep\bs{I_{\mscenario}} = \gep\bs{I}_{\gep\bs{\mscenario}}$.
    \end{example}

    \subsection{Outcome Label Symmetry}
    As demonstrated by \cref{ex:symmetries}, permutations on outcome labels can be applied to inequalities themselves to generate new inequalities. To formalize this notion, let $\Perm{S}$ denote the \term{permutation group} acting on the set $S$ consisting of all bijective maps $s : S \to S$.
    \[ \Perm{S} = \bc{s : S \to S} \]
        Then (outcome) \term{label permutation group} $\go$ for a set of random variables $\mathcal{V} = \bc{v_1, \ldots, v_n}$ is the direct product of permutations over the outcome labels for each variable $v_i \in \mathcal{V}$,
        \[ \go \defined \Perm{O_{v_1}} \times \cdots \times \Perm{O_{v_n}} = \prod_{v \in \mathcal{V}} \Perm{O_{v}} \]
        The action of $\geo \in \go$ on an outcome $f \in \Out{\mathcal{V}}$ (denoted $\geo\bs{f}$) is defined as,
        \[ \forall v \in \mathcal{V} : \br{\geo\bs{f}}\br{v} \defined \geo\bs{f\br{v}} \eq \label{eq:acto}\]
    \begin{lemma}
        \label{lem:extendable_invariance_acto}
        If a marginal outcome $m \in \Out{V} \subset \Out{\mscenario}$ is extendable to the joint outcome $j \in \Out{J}$, then $\geo\bs{m}$ is extendable to $\geo\bs{j}$ for any label permutation $\geo \in \go$.
        \[ m \ext j \iff \geo\bs{m} \ext \geo\bs{j} \eq \label{eq:extendable_invariance_acto}\]
    \end{lemma}
        The proof should be clear by the definition of extendability (\cref{def:extendable}).
        \[ m \ext j \iff \forall v \in \Dom{m} : j\br{v} = m\br{v} \]
        Since $\Dom{m} = \Dom{\geo\bs{m}}$ and by \cref{eq:acto},
        \[ \forall v \in \Dom{\geo\bs{m}}: \br{\geo\bs{j}}\br{v} = \geo\bs{j\br{v}} = \geo\bs{m\br{v}} = \br{\geo\bs{m}}\br{v} \]
        We have that $\geo\bs{m} \ext \geo\bs{j}$. The left implication of \cref{eq:extendable_invariance_acto} follows by considering $\geo^{-1} \in \go$.
        \label{coll:incidence_invariance}
        Let $M$ be the incidence matrix for a marginal scenario $\mscenario$ and $\geo \in \go$ be a label permutation of the joint random variables $\jointvar$. By \cref{lem:extendable_invariance_acto}, the action of $\geo$ on $M$ leaves $M$ invariant ($\geo\bs{M} = M$),
        \[ \geo\bs{M}_{m,j} \defined M_{\geo\bs{m},\geo\bs{j}} = \de_{\geo\bs{m} \ext \geo\bs{j}} = \de_{m \ext j} = M_{m,j} \]
    \begin{theorem}
        For each compatibility inequality $I_{\mscenario}$ and label permutation $\geo \in \go$, the inequality defined by $\geo\bs{I_{\mscenario}} = \geo\bs{I}_{\mscenario}$ is also a valid compatibility inequality for the marginal scenario $\mscenario$.
    \end{theorem}
        First let $I_{\mscenario} = \bc{\ga \cdot \probvec^{\mscenario} \geq 0}$ for the marginal scenario $\mscenario$ and $\ga$ is the certificate associated with $I_{\mscenario}$. Furthermore let $\geo\bs{I_{\mscenario}} = \geo\bs{I}_{\mscenario} = \bc{\ga \cdot \geo\bs{\probvec}^{\mscenario} \geq 0}$ be the inequality obtained after permuting $\probvec^{\mscenario}$ defined as,
        \[ \forall m \in \Out{\mscenario} : \geo\bs{\probvec}^{\mscenario}_m \defined \probvec^{\mscenario}_{\geo\bs{m}} \]
        It should be clear to see that $\geo\bs{I_{\mscenario}}$ can be rewritten as,
        \[ \ga \cdot \geo\bs{\probvec}^{\mscenario} = \sum_{m \in \supp{\ga}} \ga_{m} \probvec^{\mscenario}_{\geo\bs{m}} = \sum_{\geo^{-1}\bs{m} \in \supp{\geo^{-1}\bs{\ga}}} \ga_{\geo^{-1}\bs{m}} \probvec^{\mscenario}_{m} = \geo^{-1}\bs{\ga} \cdot \probvec^{\mscenario} \]
        Therefore the permuted inequality is equivalent to,
        \[ \geo\bs{I}_{\mscenario} = \bc{\geo^{-1}\bs{\ga} \cdot \probvec^{\mscenario} \geq 0} \]
        All that remains to be proven is that $\geo^{-1}\bs{\ga}$ forms a valid certificate for the incidence matrix $M$. Since $\geo \in \go$, then by \cref{coll:incidence_invariance},
        \[ \br{\geo^{-1}\bs{\ga} \cdot M}_j = \sum_{m \in \supp{\geo^{-1}\bs{\ga}}} \geo^{-1}\bs{\ga}_m \de_{m\ext j} = \sum_{m \in \supp{\ga}} \bs{\ga}_m \de_{\geo\bs{m}\ext j} = \sum_{m \in \supp{\ga}} \bs{\ga}_m \de_{m\ext \geo^{-1}\bs{j}} = \br{\ga \cdot M}_{\geo^{-1}\bs{j}} \]
        But since $I_{\mscenario}$ is a valid compatibility inequality, $\ga \cdot M \succeq 0$ and thus $\geo^{-1}\bs{\ga} \cdot M \succeq 0$ making $\geo\bs{I}_{\mscenario}$ a valid compatibility inequality as well.

    \subsection{Causal Symmetry}
    The aim of this section is to formalize what types of symmetries are present in a particular causal structure $\graph$. The group of these causal symmetries will define, for each compatibility inequality $I_{\mscenario}$, a family of inequalities that are also valid incompatibility inequalities.

    First consider the permutation group acting on a set of nodes $N \subseteq \nodes$ denoted $\Perm{N}$ to be the set of all bijective maps $\gep$ from $N$ to $N$.
    \[ \Perm{N} = \bc{\gep \mid \gep : N \to N} \]
    The action of $\gep \in \Perm{N}$ on a causal structure $\graph$ is defined via an the extension of $\gep$ to the corresponding element in $\Perm{\nodes}$ that leaves nodes $n \in \nodes \setminus N$ invariant,
    \begin{align*}
    \gep\bs{\graph} &\defined \br{\gep\bs{\nodes}, \gep\bs{\edges}} \\
    \gep\bs{\nodes} &\defined \bc{\gep\bs{n} \mid n \in \nodes} = \nodes \\
    \gep\bs{\edges} &\defined \bc{\gep\bs{e} \mid e \in \edges}
    \end{align*}
    To motivate a more general treatment of such symmetries, consider the Triangle Scenario of \cref{fig:triangle_scenario}. Due to the rotational and reflective symmetries of the Triangle Scenario, any permutation $\gep \in \Perm{\nodes_O}$ of the observable nodes $\nodes_O = \bc{A, B, C}$ creates a new causal structure $\gep\bs{\graph}$ that is \textit{equivalent} to $\graph$ up to a relabeling of \textit{latent} nodes. By construction, any valid compatibility inequality $I_{\mscenario}$ for the marginal scenario $\mscenario = \bc{V_1, \ldots, V_k}$ is \textit{independent} of the labeling of latent nodes. Therefore applying $\gep$ to all distributions in $I_{\mscenario}$ yields $\gep\bs{I_{\mscenario}} \defined \gep\bs{I}_{\gep\bs{\mscenario}}$, another valid compatibility inequality for the permuted marginal scenario $\gep\bs{\mscenario}$ defined as,
    \[ \gep\bs{\mscenario} = \bc{\gep\bs{V_1}, \ldots, \gep\bs{V_k}} \]
    % \begin{example}
    %     \todo[TC]{Above trivial example.}
    %     Consider the marginal scenario $V_{\bs{4}} = \bc{\bc{A,B,C}, \bc{A}, \bc{B}, \bc{C}}$ and the compatibility inequality $I_{\bc{ABC, A, B, C}}$ for the Triangle Scenario in \cref{fig:triangle_scenario} with the following form,
    %     \[ \prob[ABC][002]\prob[ABC][003] \leq \prob[A][0]\prob[C][3] \]
    %     Now consider $\gep = \bc{A \to A, B \to C, C \to B}$. Since $\gep\bs{\graph} = \graph$, $\gep\bs{I_{\mscenario}}$ is also a valid compatibility inequality,
    % \end{example}
    More generically, any permutation $\gep$ that preserves the graphical structure of $\graph$ can be applied to $I_{\mscenario}$ to generate new and valid compatibility inequalities. Specifically this alludes to the \term{graph automorphism group} $\Aut{\graph}$ of $\graph$.
    \[ \Aut{\graph} \defined \bc{\gep \in \Perm{\nodes} \mid \gep\bs{\graph} = \graph} \]
    In general, $\Aut{\graph}$ could include elements $\gep$ that map latent nodes to observable nodes\footnote{In practice however, it is rare to be considering a causal structure $\graph$ where some latent node $n_L \in \nodes_L$ takes on an role indistinguishable from some observable node $n_O \in \nodes_O$, so this won't be an issue.}. This behaviour is \textit{undesired} for causal inference where the latent nodes will never appear in a marginal scenario. Instead, the subgroup of $\Aut{\graph}$ that never maps observable nodes to latent nodes is the \term{set-wise stabilizer} of $\Aut{\graph}$ for $\nodes_O$ and will be expressed with a subscript.
